### 2017-12-12 UOW_thesis_template_v2-0/thesis_template/chapters/euroComp.tex
:art: only changes left are code and f_n derivatio

\subsection{Call-on-a-call compound option}
A call-on-a-call option, denoted by $v_{\text{cc}}$, is composed of two European call options with two different strikes $K_1$ and $K_2$ and payoffs $\phi_1(x) = \max(x - K_1, 0)$ at $T_1$ and $\phi_2(x) = \max(x - K_2, 0)$ at $T_2$, respectively. Using \eqref{eqn:v1aa}, where we identify $v_1$ with $v_\mathrm{cc}$ and $v_2$ with $v_\mathrm{c}$, we obtain
	\begin{equation*}
		v_{\text{cc}}(x,t) = \int_0^\infty \fr{1}{y} \K\left( \fr{x}{y}, t, T_1 \right)\max(v_\text{c}(y,T_1; K_2, T_2) - K_1, 0)\, \d y.
	\end{equation*}
To proceed, we assume that $v_{\text{c}}(y,T_1; K_2, T_2) > K_1$ is \emph{greater} for all $y$ greater than some critical value $y_\mathrm{c}^*$~\cite{Kwok2008}. Due to the monotonicity of a European call with respect to the asset value, this critical value $y_\mathrm{c}^*$ will always be unique (see Figure~\ref{fig:1}). This simplifies the integral to
	\begin{align*}
		v_{\text{cc}}(x,t) &= \int_{y_\mathrm{c}^*}^\infty \fr{1}{y}\K\left( \fr{x}{y}, t, T_1 \right)[v_\text{c}(y,T_1; K_2, T_2) - K_1] \, \d y \\
		&= \int_{y_\mathrm{c}^*}^\infty \fr{1}{y} \K\left( \fr{x}{y}, t, T_1 \right)v_\text{c}(y,T_1; K_2, T_2) \, \d y - K_1\int_{y_\mathrm{c}^*}^\infty \fr{1}{y}\K\left( \fr{x}{y}, t, T_1 \right) \, \d y.
	\end{align*}

@@

\section{Generalised example: straddle-on-a-call compound option}
We outlined in Section~\ref{sec:gen} that the results in Corollary 1 can be implemented for any financial payoff in options pricing to generate any compound option pricing formula. This is attainable since any of the aforementioned payoffs can be expressed as finite linear combinations of the functions
	\begin{equation}
		\label{eqn:funcs}
		x \mapsto \1_I(x), \quad x \mapsto x\1_I(x),
	\end{equation}
where $\1_I$ is the indicator function defined as
	\begin{equation*}
		\1_I(x) = \begin{cases}
			1, \quad x \in I, \\
			0, \quad x \notin I,
		\end{cases}
	\end{equation*}
and where $I$ is an arbitrary interval with endpoints $a$ and $b$ with $a < b$. The interval can be open, half-closed, or closed. The two auxiliary functions in~\eqref{eqn:funcs} are the building blocks for many possible financial payoffs in options pricing. For example, a call option has a payoff $\max(x-K,0)$ which can be written as
	\begin{equation*}
		\max(x-K,0) = x\1_{[K,\infty)}(x) - K\1_{[K,\infty)}(x),
	\end{equation*}
where the interval $I$ is $[K,\infty)$.

@@

In general, the underlying asset with a potential dividend yield (whether discrete or continuous) is governed by~\cite{Wilmott1995}
	\begin{equation*}
		%\label{eqn:SDE2}
		\d S_t = [r(t)S_t - D(S_t,t)] \, \d t + \sigma(t) S_t  \, \d W_t,
	\end{equation*}
where $D(S_t,t)$ does not necessarily to have be linear in $S_t$. It follows that a European option whose underlying follows the SDE above satisfies
	\begin{equation*}
		\fr{\pr v}{\pr t} + \fr{1}{2}\sigma(t)^2x^2\fr{\pr^2 v}{\pr x^2} + [r(t)x - D(x,t)]\fr{\pr v}{\pr x} - r(t)v = 0.
	\end{equation*}
This is a potential unified approach to pricing options regardless of whether the dividend yield is continuous or discrete. However, the Black-Scholes kernel identities in the preliminaries rely on the dividend term $D$ being linear in $x$ (i.e., $D(x,t) = q(t)x$). Therefore, in order to adapt the kernel identities, we have assumed a specific form for $D$ to be able to construct a pricing formula for discrete dividends.

>>>>

\subsection{Call-on-a-call compound option}
A call-on-a-call option, denoted by $v_{\text{cc}}$, is composed of two European call options with two different strikes $K_1$ and $K_2$ and payoffs $\phi_1(x) = \max(x - K_1, 0)$ at $T_1$ and $\phi_2(x) = \max(x - K_2, 0)$ at $T_2$, respectively. Using \eqref{eqn:v1aa}, where we identify $v_1$ with $v_\mathrm{cc}$ and $v_2$ with $v_\mathrm{c}$, we obtain
	\begin{equation*}
		v_{\text{cc}}(x,t) = \int_0^\infty \fr{1}{y} \K\left( \fr{x}{y}, t, T_1 \right)\max(v_\text{c}(y,T_1; K_2, T_2) - K_1, 0)\, \d y.
	\end{equation*}
To proceed, we assume that $v_{\text{c}}(y,T_1; K_2, T_2) > K_1$ for all $y$ greater than some critical value $y_\mathrm{c}^*$~\cite{Kwok2008}. Due to the monotonicity of a European call with respect to the asset value, this critical value $y_\mathrm{c}^*$ will always be unique (see Figure~\ref{fig:1}). This simplifies the integral to
	\begin{align*}
		v_{\text{cc}}(x,t) &= \int_{y_\mathrm{c}^*}^\infty \fr{1}{y}\K\left( \fr{x}{y}, t, T_1 \right)[v_\text{c}(y,T_1; K_2, T_2) - K_1] \, \d y \\
		&= \int_{y_\mathrm{c}^*}^\infty \fr{1}{y} \K\left( \fr{x}{y}, t, T_1 \right)v_\text{c}(y,T_1; K_2, T_2) \, \d y - K_1\int_{y_\mathrm{c}^*}^\infty \fr{1}{y}\K\left( \fr{x}{y}, t, T_1 \right) \, \d y.
	\end{align*}

@@

\section{Generalised example: straddle-on-a-call compound option}
We outlined in Section~\ref{sec:gen} that the results in Corollary 1 can be implemented for any financial payoff in options pricing to generate any compound option pricing formula. This is attainable since any of the aforementioned payoffs can be expressed as finite linear combinations of the functions
	\begin{equation}
		\label{eqn:funcs}
		x \mapsto \1_I(x), \quad x \mapsto x\1_I(x),
	\end{equation}
where $\1_I$ is the indicator function defined as
	\begin{equation*}
		\1_I(x) = \begin{cases}
			1, \quad x \in I, \\
			0, \quad x \notin I,
		\end{cases}
	\end{equation*}
and where $I$ is an arbitrary interval with endpoints $a$ and $b$ with $a < b$. The interval can be open, half-closed, or closed. \textcolor{blue}{The two auxiliary functions in~\eqref{eqn:funcs} are the building blocks for many financial payoffs in options pricing.} For example, a call option has a payoff $\max(x-K,0)$ which can be written as
	\begin{equation*}
		\max(x-K,0) = x\1_{[K,\infty)}(x) - K\1_{[K,\infty)}(x),
	\end{equation*}
where the interval $I$ is $[K,\infty)$.

@@

The underlying asset with a potential dividend yield (whether discrete or continuous) is governed by~\cite{Wilmott1995}
	\begin{equation*}
		%\label{eqn:SDE2}
		\d S_t = [r(t)S_t - D(S_t,t)] \, \d t + \sigma(t) S_t  \, \d W_t,
	\end{equation*}
where $D(S_t,t)$ does not necessarily to have be linear in $S_t$. It follows that a European option whose underlying follows the SDE above satisfies
	\begin{equation*}
		\fr{\pr v}{\pr t} + \fr{1}{2}\sigma(t)^2x^2\fr{\pr^2 v}{\pr x^2} + [r(t)x - D(x,t)]\fr{\pr v}{\pr x} - r(t)v = 0.
	\end{equation*}
This is a potential unified approach to pricing options regardless of whether the dividend yield is continuous or discrete. However, the Black-Scholes kernel identities in the preliminaries rely on the dividend term $D$ being linear in $x$ (i.e., $D(x,t) = q(t)x$). Therefore, in order to adapt the kernel identities, we have assumed a specific form for $D$ to be able to construct a pricing formula for discrete dividends.

### 2017-12-12 UOW_thesis_template_v2-0/thesis_template/chapters/jumpImpVol.tex
:art: only changes left are code and f_n derivatio

\subsection{Derivation of a Dupire-like PIDE via Euler's theorem on homogeneous functions}
The partial derivatives of the Dupire equation~\cite{Gatheral2006} are with respect to the strike price $K$. Thus to derive a Dupire-like PIDE, we will require partial derivatives in terms of $x'$ (the analogous variable for $K$). This can be done by invoking Euler's theorem for homogeneous functions~\cite[pp. 317]{Kishan2007} to $v$ and we get
	\begin{equation*}
		x\fr{\pr v}{\pr x} + x'\fr{\pr v}{\pr x'} = v,
	\end{equation*}
since $v$ has been shown to be homogeneous in $x$ and $x'$ of degree one. By differentiating the above equation with respect to $x$ and $x'$, we obtain
	\begin{equation*}
		x\fr{\pr^2 v}{\pr x^2} = -x'\fr{\pr^2 v}{\pr x \pr x'}, \quad x'\fr{\pr^2 v}{\pr x'^2} = -x\fr{\pr^2 v}{\pr x' \pr x},
	\end{equation*}
respectively. Hence it follows that
	\begin{equation*}
		x^2\fr{\pr^2 v}{\pr x^2} = x'^2\fr{\pr^2 v}{\pr x'^2}.
	\end{equation*}
The only term left to account for is the integral in (\ref{eqn:PIDE}). Notice that the first integrand term depends on~$y$; we want to transfer the dependency on $y$ to the third argument (i.e., $x'$). This can be achieved by the homogeneity property in (\ref{eqn:homogen}), and we obtain
	\begin{align*}
		v(xy,t; x') &= v\left(xy,t;\fr{x'y}{y}\right) = yv\left( x,t;\fr{x'}{y} \right).
	\end{align*}
Thus, setting $u(x',t; x) = v(x,t; x')$ and replacing all the $x$ derivatives with $x'$ derivatives and substituting the above rearrangement for the integrand, we get
	\begin{align}
		\label{eqn:DupireLike}
		\begin{split}
		\fr{\pr u}{\pr t} &- (q(t) + \kappa\lambda)u - (r(t) - q(t) - \kappa\lambda)x'\fr{\pr u}{\pr x'} + \fr{1}{2}\sigma(t)^2x'^2\fr{\pr^2 u}{\pr x'^2} \\
		& {} + \lambda \int_0^\infty \left( yu\left( \fr{x'}{y},t; x \right) - u(x',t; x) \right)f(y) \, \d y = 0
		\end{split}
	\end{align}
with
	\begin{equation}
		\label{eqn:DupireCond}
		u(x',T; x) = \phi(x';x),
	\end{equation}
since $u$ now depends on the variables $x'$ and $t$ with $x$ as a parameter. Equations~(\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}) together form the Dupire-like PIDE system for options in a jump-diffusion framework. Note that this reduces to the standard Dupire PDE as seen in \cite{Gatheral2006} in the absence of jumps (i.e., $\lambda = 0$) when $\phi$ is either the call or put payoff.

>>>>

\subsection{Derivation of a Dupire-like PIDE via Euler's theorem on homogeneous functions}
The partial derivatives of the Dupire equation~\cite{Gatheral2006} \textcolor{blue}{are with respect to the strike price $K$.} Thus to derive a Dupire-like PIDE, we will require partial derivatives in terms of $x'$ (the analogous variable for $K$). This can be done by invoking Euler's theorem for homogeneous functions~\cite[pp. 317]{Kishan2007} to $v$ and we get
	\begin{equation*}
		x\fr{\pr v}{\pr x} + x'\fr{\pr v}{\pr x'} = v,
	\end{equation*}
since $v$ has been shown to be homogeneous in $x$ and $x'$ of degree one. By differentiating the above equation with respect to $x$ and $x'$, we obtain
	\begin{equation*}
		x\fr{\pr^2 v}{\pr x^2} = -x'\fr{\pr^2 v}{\pr x \pr x'}, \quad x'\fr{\pr^2 v}{\pr x'^2} = -x\fr{\pr^2 v}{\pr x' \pr x},
	\end{equation*}
respectively. Hence it follows that
	\begin{equation*}
		x^2\fr{\pr^2 v}{\pr x^2} = x'^2\fr{\pr^2 v}{\pr x'^2}.
	\end{equation*}
The only term left to account for is the integral in (\ref{eqn:PIDE}). Notice that the first integrand term depends on~$y$; we want to transfer the dependency on $y$ to the third argument (i.e., $x'$). This can be achieved by the homogeneity property in (\ref{eqn:homogen}), and we obtain
	\begin{align*}
		v(xy,t; x') &= v\left(xy,t;\fr{x'y}{y}\right) = yv\left( x,t;\fr{x'}{y} \right).
	\end{align*}
Thus, setting $u(x',t; x) = v(x,t; x')$ and replacing all the $x$ derivatives with $x'$ derivatives and substituting the above rearrangement for the integrand, we get
	\begin{align}
		\label{eqn:DupireLike}
		\begin{split}
		\fr{\pr u}{\pr t} &- (q(t) + \kappa\lambda)u - (r(t) - q(t) - \kappa\lambda)x'\fr{\pr u}{\pr x'} + \fr{1}{2}\sigma(t)^2x'^2\fr{\pr^2 u}{\pr x'^2} \\
		& {} + \lambda \int_0^\infty \left( yu\left( \fr{x'}{y},t; x \right) - u(x',t; x) \right)f(y) \, \d y = 0
		\end{split}
	\end{align}
with
	\begin{equation}
		\label{eqn:DupireCond}
		u(x',T; x) = \phi(x';x),
	\end{equation}
since $u$ now depends on the variables $x'$ and $t$ with $x$ as a parameter. Equations~(\ref{eqn:DupireLike}) and (\ref{eqn:DupireCond}) together form the Dupire-like PIDE system for options in a jump-diffusion framework. Note that this reduces to the standard Dupire PDE as seen in \cite{Gatheral2006} in the absence of jumps (i.e., $\lambda = 0$) when $\phi$ is either the call or put payoff.

### 2017-12-12 UOW_thesis_template_v2-0/thesis_template/chapters/jumpdiffAmer.tex
:art: only changes left are code and f_n derivatio

        where $F$ and $g$ are the inverse Mellin transforms of $\tilde F$ and $\tilde g$, respectively. We have purposefully expanded the convolution term to its integral form as this makes the next step much easier to see. The point of introducing $\tilde F$ is because, upon inversion, this term itself is another convolution. That is,

@@

		To calculate $I_{2,a}$, we swap the integrals with respect to $z$ and $w$ and using the properties of the Dirac delta function gives us

@@

		The integral $I_2$ follows a similar path for the lemmas and techniques used in deriving the analogous term with the American put. The lengthy calculations will be omitted, but the result is
        	\begin{equation}
        		\label{eqn:I2put}
        		I_2 = qx  \ds\sum\limits_{n=0}^{\infty}\int_t^T   \fr{(\lambda(u-t))^n}{n!} e^{n\mu_Y + n\sigma_Y^2/2} e^{(q+\lambda + \kappa\lambda)(u-t)} N\left( D_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u,
        	\end{equation}
	with $D_n$ defined in~\eqref{eqn:Dn}. 
	However, we will be providing the complete derivation and solution of $I_3$ as this term is rather complicated. As we will see, the result of $I_3$ will be a double integral which is more ideal to work with in comparison to a quadruple integral.

@@

        	For the American put option, we use~\eqref{eqn:amerPasting} and so have two conditions at our disposal. We will derive both of them. First we incorporate $v_{\text{a}}^{\text{put}}(S^*(t),t) = K - S^*(t)$ and we set $x = S^*(t)$ in~\eqref{eqn:amerJumpPut} to get
        	\begin{equation}
        		\label{eqn:inteqn1}
        		\begin{split}
        		K - S^*(t) = v_{\text{e}}^{\text{put}}(S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}g_p\left(\fr{S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
        		\end{split}
        	\end{equation}
        	Eq.~\eqref{eqn:inteqn1} may initially appear to be a simple implicit equation for $S^*(t)$, but the hidden layer of complication lies in the function $g_p$ that contains the other unknown $v_{\text{a}}^{\text{put}}$. Thus if the American put option pricing problem for jump-diffusion processes were to be solved numerically, one would have to solve the~\eqref{eqn:amerJumpPut} and~\eqref{eqn:inteqn1} simultaneously. As we mentioned in the introduction, a scheme to solve this linked integral equation system was reported in~\cite{Chiarella2006}. Alternatively, we may use the other value-matching condition of $\fr{\pr v_{\text{a}}^{\text{put}}}{\pr x}(S^*(t),t) = -1$ to provide us with another integral equation for $S^*(t)$. Taking the partial derivative of~\eqref{eqn:amerJumpPut} with respect to $x$, we get
        	$$
        		\fr{\pr v_{\text{a}}^{\text{put}}}{\pr x}( x, t) = \fr{\pr v_{\text{e}}^{\text{put}}}{\pr x}\left(x,t\right) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_p}{\pr x}\left(\fr{x}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
        	$$
Then we evaluate this expression at $x = S^*(t)$ to find
		\begin{equation}
			\label{eqn:inteqn2}
			\begin{split}
			-1 &=  \fr{\pr v_{\text{e}}^{\text{put}}}{\pr x}( S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_p}{\pr x}\left(\fr{ S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u) \\
			&\qquad\qquad\qquad\qquad\qquad\qquad \times \K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
			\end{split}
		\end{equation}
Similarly for the American call option and using~\eqref{eqn:amerPastingCall}, we would obtain the following:
		\begin{equation}
        		\label{eqn:inteqn3}
        		\begin{split}
        		S^*(t) - K = v_{\text{e}}^{\text{call}}(S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}g_c\left(\fr{S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u,
        		\end{split}
        	\end{equation}
 		\begin{equation}
			\label{eqn:inteqn2}
			\begin{split}
			1 &=  \fr{\pr v_{\text{e}}^{\text{call}}}{\pr x}( S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_c}{\pr x}\left(\fr{ S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u) \\
			&\qquad\qquad\qquad\qquad\qquad\qquad \times \K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
			\end{split}
		\end{equation}

@@

        	\section{Approximate integro-differential equation to the free boundary for American options in jump-diffusion dynamics}
        	We could not solve the American option pricing problem along with its respective integral equations as demonstrated in the previous section due to the difficulty in determining $S^*$. Several numerical methods exist that have yielded quite positive results (e.g., see~\cite{Kallast2003} and~\cite{Chiarella2006}), but these often can be quite complex in implementation if minor details are omitted from the expositions. Thus in a similar manner to~\cite{Rodrigo2013} where an approximate ODE was found, we will derive an approximation for the free boundary $S^*$, except now we will be examining it in a jump-diffusion framework so the ODE will now be an integro-differential equation (IDE). The numerical results from~\cite{Rodrigo2013} for the standard diffusion dynamics in the asset price showed to be accurate when compared against widely accepted techniques for computing the American option value (e.g., the binomal method).

@@

	where we split the integral in $y$ at $y=1$ because this is the value that could determine if the quantity $z = yS^*(t)$ would place $v_{\text{a}}^{\text{put}}(z,t)$ in the continuation or exercise region. We have also given them temporary names $I_1$ and $I_2$ for ease of reference. We can immediately eliminate $I_2$ since it will decay to 0. This is because in this region, $y \in (1,\infty)$, and then this implies that $yS^*(t) > S^*(t)$. So the $z$ domain of $z \in (yS^*(t),\infty)$ by default is a subset of $z \in (S^*(t),\infty)$, which is precisely the continuation region. Hence $I_2$ will be 0 because 

@@

One of the traditional FDMs used in options pricing uses a few change of variables in order to change the PDE (or PIDE) to resemble the typical heat equation. Whilst this may be more elegant, we believe it is quite easy to lose track of the current variable space. Furthermore, it can be cumbersome to visualize these results because the original problem has been altered through these variable changes. Hence we will constrain our analysis to the original variables contained within the problem.

>>>>

        where $F$ and $g$ are the inverse Mellin transforms of $\tilde F$ and $\tilde g$, respectively. We have purposefully expanded the convolution term to its integral form as this makes the next step much easier to see. The point of introducing $\tilde F$ is \textcolor{blue}{because, upon inversion,} this term itself is another convolution. That is,

@@

		To calculate $I_{2,a}$, we swap the integrals with respect to $z$ and $w$ and \textcolor{blue}{using the properties of the Dirac delta function} gives us

@@

		The integral $I_2$ follows a similar path for the lemmas and techniques used in deriving the analogous term with the American put. The lengthy calculations will be omitted, but the result is
        	\begin{equation}
        		\label{eqn:I2put}
        		I_2 = qx  \ds\sum\limits_{n=0}^{\infty}\int_t^T   \fr{(\lambda(u-t))^n}{n!} e^{n\mu_Y + n\sigma_Y^2/2} e^{(q+\lambda + \kappa\lambda)(u-t)} N\left( D_n \left( \fr{x}{S^*(u)},t,u  \right) \right) \, \d u,
        	\end{equation}
	with $D_n$ defined in~\eqref{eqn:Dn}. 
	However, we will be providing the complete derivation and solution of $I_3$ \textcolor{blue}{as this term is rather complicated.} As we will see, the result of $I_3$ will be a double integral which is more ideal to work with in comparison to a quadruple integral.

@@

        	For the American put option, we use~\eqref{eqn:amerPasting} and so have two conditions at our disposal. We will derive both of them. First we incorporate $v_{\text{a}}^{\text{put}}(S^*(t),t) = K - S^*(t)$ and we set $x = S^*(t)$ in~\eqref{eqn:amerJumpPut} to get
        	\begin{equation}
        		\label{eqn:inteqn1}
        		\begin{split}
        		K - S^*(t) = v_{\text{e}}^{\text{put}}(S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}g_p\left(\fr{S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
        		\end{split}
        	\end{equation}
        	Eq.~\eqref{eqn:inteqn1} may initially appear to be a simple implicit equation for $S^*(t)$, but the hidden layer of complication lies in the function $g_p$ that contains the other unknown $v_{\text{a}}^{\text{put}}$. Thus if the American put option pricing problem for jump-diffusion processes were to be solved numerically, one would have to solve the~\eqref{eqn:amerJumpPut} and~\eqref{eqn:inteqn1} simultaneously. As we mentioned in the introduction, a scheme to solve this linked integral equation system was \textcolor{blue}{reported in~\cite{Chiarella2006}.} Alternatively, we may use the other value-matching condition of $\fr{\pr v_{\text{a}}^{\text{put}}}{\pr x}(S^*(t),t) = -1$ to provide us with another integral equation for $S^*(t)$. Taking the partial derivative of~\eqref{eqn:amerJumpPut} with respect to $x$, we get
        	$$
        		\fr{\pr v_{\text{a}}^{\text{put}}}{\pr x}( x, t) = \fr{\pr v_{\text{e}}^{\text{put}}}{\pr x}\left(x,t\right) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_p}{\pr x}\left(\fr{x}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
        	$$
Then we evaluate this expression at $x = S^*(t)$ to find
		\begin{equation}
			\label{eqn:inteqn2}
			\begin{split}
			-1 &=  \fr{\pr v_{\text{e}}^{\text{put}}}{\pr x}( S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_p}{\pr x}\left(\fr{ S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u) \\
			&\qquad\qquad\qquad\qquad\qquad\qquad \times \K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
			\end{split}
		\end{equation}
Similarly for the American call option and using~\eqref{eqn:amerPastingCall}, we would obtain the following:
		\begin{equation}
        		\label{eqn:inteqn3}
        		\begin{split}
        		S^*(t) - K = v_{\text{e}}^{\text{call}}(S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}g_c\left(\fr{S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u)\K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u,
        		\end{split}
        	\end{equation}
 		\begin{equation}
			\label{eqn:inteqn2}
			\begin{split}
			1 &=  \fr{\pr v_{\text{e}}^{\text{call}}}{\pr x}( S^*(t),t) + \int_t^T \int_0^\infty \int_0^\infty \fr{1}{z}\fr{\pr g_c}{\pr x}\left(\fr{ S^*(t)}{z},u\right) \fr{1}{w}\J(w,t,u) \\
			&\qquad\qquad\qquad\qquad\qquad\qquad \times \K_\lambda\left( \fr{z}{w},t,u \right) \, \d w \, \d z \, \d u.
			\end{split}
		\end{equation}

@@

        	\section{Approximate integro-differential equation to the free boundary for American options in jump-diffusion dynamics}
        	We could not solve the American option pricing problem along with its respective integral equations as demonstrated in the previous section due to the difficulty in determining $S^*$. Several numerical methods exist that have \textcolor{blue}{yielded quite positive results} (e.g., see~\cite{Kallast2003} and~\cite{Chiarella2006}), but these often can be quite complex in implementation if minor details are omitted from the expositions. Thus in a similar manner to~\cite{Rodrigo2013} where an approximate ODE was found, we will derive an approximation for the free boundary $S^*$, except now we will be examining it in a jump-diffusion framework so the ODE will now be an integro-differential equation (IDE). The numerical results from~\cite{Rodrigo2013} for the standard diffusion dynamics in the asset price \textcolor{blue}{showed to be accurate} when compared against widely accepted techniques for computing the American option value (e.g., the binomal method).

@@

	where we split the integral in $y$ at $y=1$ because this is the value that \textcolor{blue}{could} determine if the quantity $z = yS^*(t)$ would place $v_{\text{a}}^{\text{put}}(z,t)$ in the continuation or exercise region. We have also given them temporary names $I_1$ and $I_2$ for ease of reference. We can immediately eliminate $I_2$ since it will decay to 0. This is because in this region, $y \in (1,\infty)$, and then this implies that $yS^*(t) > S^*(t)$. So the $z$ domain of $z \in (yS^*(t),\infty)$ by default is a subset of $z \in (S^*(t),\infty)$, which is precisely the continuation region. Hence $I_2$ will be 0 because 

@@

\textcolor{blue}{One of the traditional FDMs used in options pricing uses a few change of variables in order to change the PDE (or PIDE) to resemble the typical heat equation.} Whilst this may be more elegant, we believe it is quite easy to lose track of the current variable space. Furthermore, it can be cumbersome to visualize these results because the original problem has been altered through these variable changes. Hence we will constrain our analysis to the original variables contained within the problem.
